### 2020-08-21 sections/experience.tex
Create experience.tex

\cvsection{Expertise}

\begin{cvskills}

\cvskill
{Interests}
{Cabinets composition and allocation, ministerial turnover, political elites socialisation, civil service}

\cvskill
{}
{systems, political participation, digital media, electronic government}\\

\cvskill
{Techniques} 
{Survival analysis, regression modelling, multilevel models, factor analysis, spatial analysis, social}

\cvskill
{} 
{network analysis, qualitative comparative analysis, topic modelling} \\

\end{cvskills}

>>>>

\cvsection{Relevant Employment}

\begin{cventries}
\cventry
{Instructor} 
{Universidad de Santiago} 
{Santiago, Chile} 
{2018 - on leave}
{Department of Public Administration and Policy, Faculty of Economics and Management}\vspace{1.5mm}

\cventry
{Consultant} 
{United Nations Development Programme} 
{Santiago, Chile} 
{2016 - 2017}
{Democratic Governance Programme} \vspace{1.5mm}

\cventry
{Adjunct Professor} 
{Universidad de Santiago} 
{Santiago, Chile} 
{2014 - 2017}
{Department of Public Administration and Policy, Faculty of Economics and Management} \vspace{1.5mm}

\end{cventries}
